---
title: "Peer Teaching Program 2022"
output: html_notebook
---

## Designed by rudrakshkarpe


```{r}
plot(cars)
```


Data Frames in the R in R programming language

Data Frames in R Language are generic data objects of R which are used to store the tabular data. Data frames can also be interpreted as matrices where each column of a matrix can be of the different data types. Data Frame is made up of three principal components, the data, rows, and columns.

# two methods 

Method 1 -> select the file manually 

- using the File choose function file.choose()

```{r}

stats <- read.csv(file.choose())

```



Method 2 -> we set the working directory and we'll read the data ROM there

working directory explanation

```{r}
getwd()


# windows
# setwd("C:\\Users\\rudra\\OneDrive\\Desktop\\")
  
# Mac
  
# setwd("/users/rudrakshkarpe/desktop/")
```


To remove the previously loaded data for the stats variable
# rm(stats)


# Exploring the data sets

stats


```{r}
# to check the number of rows in the imported data set

nrow(stats)
```


```{r}
# to check the number of colums from the imported dataset

ncol(stats)

```


```{r}
# to get the top six rows

head(stats)


```



```{r}

# bottom six rows 

tail(stats, n = 10)


```

```{r}
# strings represnted in the numeric values ACSII

str(stats)
```


# str() and runif() functions

# str() --> R programming language it sands for structure

# runif()  --> Randon variables distributed uniformly

# 



```{r}

# summery of every single coloumn is some different way 

summary(stats)
```
# Using the $ sign


```{r}
stats

head(stats)

stats[3,3]
stats[3,"Deaths"]

# stats["Recovered",3] you can't do this with the column 

# $ sign is another way to access the data from the data frame
# stats#column_name
stats$Recovered
# stats[, "Recovered"] similar operation with the opration with the dollar sign
# stats$Recovered[2
```

# level function to get more form the coloumn extacted

```{r}
levels(stats$Recovered)


```


