---
title: "R Notebook"
output: html_notebook
Aurthor: rudrakshkarpe
---

## Hello everyone. Here, I'll be covering *core programming concepts* for the R prgramming Language.

### You can follow the complete Notebook!!
### Types of variables in R programming langauge
```{r}
# interger

x <- 2 

# to make it interger keep it like 2L

typeof(x)

# double

y <- 2.5  # decimal point 
typeof(y)


# double mode is default mode in
# R programming langauge

# complex

z <- 3 +2i
  
typeof(z)

# character

a <- "Rudraksh"

typeof(a)

# logical 

q1 <- T

typeof(q1)
```


```{r}
A <- 10
B <- 5

c <- A+B

# printing out the variable

c

variable1 <- 2.5
variable2 <- 4

sum <- variable1 / variable2
sum

# That is how you implement the code using the new programs

answer <- sqrt(variable2)
answer
```


### Operations on the character operator

```{r}
greetings <- "Hello"

name <- "Rudraksh"

Message <- paste(greetings, name)
Message
```

### Logical variables and operators


```{r}
# TRUE  or T

# FALSE or F


4 < 5
7 == 7
7 != 0
7 <= 0
8 >= 9

# &
# isTRUE(x)

result1 <- 4 < 5
result1  

result2 <- 9 < 0
result2


result1 | result2

result1 & result2



```

## Loops in R programming   

- While Loop
  -Not widely used in the programming languages like R

```{r}



# if the logical expression turns true then the body of the loop
# will get executed
# in order to stop the infinite loop type escape

while(FALSE){
 # body of the loop
  print("Hello THere! This is rudraksh!")
  
}

counter <- 1
while (counter < 12){
  print(counter)
  counter <- counter + 1
}

counter <- 1
while(counter <= 10){
  print("Rudraksh is a Programmer")
  counter <- counter + 1 
}

## using counter you can iterate with the loop

```


## For Loop

## vectors in R programming 

### This is where we gonna encounter vectors 1:5 is basically a vector here

### it's basically a vector of numbers in other programming languages we call it array



```{r}
# while loop
counter <- 1
while(counter <= 10){
  print("Rudraksh is a Programmer")
  counter <- counter + 1 
}


for(i in 1:5){
  print("Hello R Programming!")
}

for(rudra in 1:10){
  print("R")
}
 

1:5  


```

### If statements in R programming Language

```{r}
# rnorm function generates the random numbers

# rm(ans)
# x <- rnorm(1)
if(x > 1){
  ans <- "Greater than 1!"
  print(ans)
  
}else{
  # has no parentheses cuz it's default statement it doesn't require condition
  answer <- "Less than 1"
  print(answer)

  # if(x>= -1){
  #   ans <- "Between -1 and 1"
  # }else{
  #   ans <- "Less than 1"
  # }
```


### Why all the lines are always copied to the cosole?
- It can simply make your life easy, you can type the code itself in the console using this utility.





























