---
title: "R Notebook"
output: html_notebook
Aurthor: rudrakshkarpe
---

## Hello everyone. Here, I'll be covering *core programming concepts* for the R prgramming Language.

### You can follow the complete Notebook!!
### Types of variables in R programming langauge
```{r}
# interger

x <- 2 

# to make it interger keep it like 2L

typeof(x)

# double
```


  

```{r}
y <- 2.5  # decimal point 
typeof(y)


# double mode is default mode in
# R programming langauge

# complex

z <- 3 +2i
  
typeof(z)

# character

a <- "Rudraksh"

typeof(a)

# logical 

q1 <- T

typeof(q1)
```


```{r}
A <- 10
B <- 5

c <- A+B

# printing out the variable

c

variable1 <- 2.5
variable2 <- 4

sum <- variable1 / variable2
sum

# That is how you implement the code using the new programs

answer <- sqrt(variable2)
answer
```


### Operations on the character operator

```{r}
greetings <- "Hello"

name <- "Rudraksh"

Message <- paste(greetings, name)
Message
```

### Logical variables and operators


```{r}
# TRUE  or T

# FALSE or F


4 < 5
7 == 7
7 != 0
7 <= 0
8 >= 9

# &
# isTRUE(x)

result1 <- 4 < 5
result1  

result2 <- 9 < 0
result2


result1 | result2

result1 & result2



```

## Loops in R programming   

- While Loop
  -Not widely used in the programming languages like R

```{r}



# if the logical expression turns true then the body of the loop
# will get executed
# in order to stop the infinite loop type escape
# 
# while(FALSE){
#  # body of the loop
#   print("Hello THere! This is rudraksh!")
#   
# }

counter <- 1
while (counter <= 12){
  print(counter)
  counter <- counter + 1
}

# counter <- 1
# while(counter <= 10){
#   print("Rudraksh is a Programmer")
#   counter <- counter + 1 
# }
  
## using counter you can iterate with the loop

```
```{r}
# New chunk added
```


## For Loop

## vectors in R programming 

### This is where we gonna encounter vectors 1:5 is basically a vector here

### it's basically a vector of numbers in other programming languages we call it array



```{r}
# while loop
# counter <- 1
# while(counter <= 10){
#   print("Rudraksh is a Programmer")
#   counter <- counter + 1 
# }


for(i in 1:20){
  print("Peer Teaching program 2022")
}

# for(rudra in 1:10){
#   print("R")
# }
#  

# 1:5  


```

### If statements in R programming Language

```{r}


rm(ans)
x <- rnorm(1)
if(x > 1){
  ans <- "Greater than 1!"
  print(ans)
  
}else{
  answer <- "Less than 1  ->> This is not expected!"
  print(answer)
}
  
```


### Why all the lines are always copied to the cosole?
- It can simply make your life easy, you can type the code itself in the console using this utility.





























